Title Goes Here

### 2019-03-30 analysis/paper/paper.Rmd
move some code to the tidy-data chunk

ornaments_period <- 
kwl_upper %>% 
  filter(!is.na(`6-layers`)) %>% 
  mutate(period = case_when(
    `6-layers` %in% 1:2 ~ "Chinese Contact",
    `6-layers` == 4 ~ "European Contact",
    `6-layers` %in% 5:6 ~ "Before European Contact",
     TRUE ~ "other"
  )) %>% 
  filter(period != "other") %>% 
  mutate(period = factor(period,
                       level = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))
```

@@

ornaments_count_test <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  group_by(Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

@@

```{r scatter-plot-bead-by-period}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`),
         Perforation1 = as.numeric(`Perforation1(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1`, `Perforation2(mm)`), 
                               na.rm = TRUE))

@@

# plot for intact agate bead by period
ornaments_intact_agate <-
  ornaments_period %>% 
  filter(Condition %in% c('complete','near-complete'),
         Categories == 'Agate bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

@@

```{r scatter-plot-metal-by-period}
# plot for intact bell by period
ornaments_intact_bell <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Bell',
         Type != 'unclassified') %>% 
  mutate(Length = as.numeric(gsub("\\+", "", `Length(mm)`)), #remove +
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`))

@@

# plot for intact ring by period
ornaments_intact_ring <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Metal ring') %>% 
  mutate(Length = as.numeric(gsub("\\+|\\-", "", `Length(mm)`)), #remove + -
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`))

@@

```{r-gganimate}
devtools::install_github('thomasp85/gganimate')
library(gganimate)

@@

anim_gold_bead_spatial <-
  ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  transition_states(period, 3, 1) +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

>>>>

ornaments_period <- 
kwl_upper %>% 
  filter(!is.na(`6-layers`)) %>% 
  mutate(period = case_when(
    `6-layers` %in% 1:2 ~ "Chinese Contact",
    `6-layers` == 4 ~ "European Contact",
    `6-layers` %in% 5:6 ~ "Before European Contact",
     TRUE ~ "other"
  )) %>% 
  filter(period != "other") %>% 
  mutate(period = factor(period,
                       level = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact"))) %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`),
         Perforation1 = as.numeric(`Perforation1(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1`, `Perforation2(mm)`), 
                               na.rm = TRUE))
```

@@

ornaments_count_test <-
  ornaments_period %>% 
  filter(!is.na(`6-layers`),
         Categories != "Unknown Metal") %>% 
  mutate(Categories = as.factor(Categories)) %>% 
  mutate(Categories = fct_lump(Categories, 
                               n = 5)) %>% 
  group_by(Categories) %>%
  count() %>% 
  ungroup() %>% 
  mutate(Categories = fct_reorder(Categories, n))

@@

```{r scatter-plot-bead-by-period}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead')

@@

# plot for intact agate bead by period
ornaments_intact_agate <-
  ornaments_period %>% 
  filter(Condition %in% c('complete','near-complete'),
         Categories == 'Agate bead')

@@

```{r scatter-plot-metal-by-period}
# plot for intact bell by period
ornaments_intact_bell <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Bell',
         Type != 'unclassified') %>% 
  mutate(Length = as.numeric(gsub("\\+", "", `Length(mm)`))) #remove +

@@

# plot for intact ring by period
ornaments_intact_ring <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Metal ring') %>% 
  mutate(Length = as.numeric(gsub("\\+|\\-", "", `Length(mm)`))) #remove + -

@@

```{r-gganimate}
# test gganimate for measurement of beads by period
devtools::install_github('thomasp85/gganimate')
library(gganimate)

@@

# does not work
anim_gold_bead_spatial <-
  ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  transition_states(period, 3, 1) +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
